### 2012-06-28 inst/examples/bh_uniform.Rmd
cleaner plots

``` {r }
pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
````

@@

``` {r sethiplots, rerun=TRUE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
  ylab("escapement")

ggplot(policy) +
  geom_point(aes(stock, x_grid[value], color=variable)) +
	geom_smooth(aes(stock, x_grid[value], color=variable)) +
  ylab("harvest")

@@

ggplot(value) + 
  geom_point(aes(stock, value, color=variable)) +
  geom_smooth(aes(stock, value, color=variable)) +
  ylab("Net Present Value")
````

>>>>

``` {r }
pars <- c(A, B)
K <- (pars[1] - 1)/pars[2]
````

@@

``` {r sethiplots}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value], color=variable), shape='+') +
	stat_smooth(aes(stock, stock-x_grid[value], color=variable), 
    degree=1, se=FALSE, span=0.3) +
  ylab("escapement")

ggplot(policy) +
  geom_point(aes(stock, x_grid[value], color=variable), shape='+') +
	stat_smooth(aes(stock, x_grid[value], color=variable),
    degree=1, se=FALSE, span=0.3) +
  ylab("harvest")

@@

ggplot(value) + 
  geom_point(aes(stock, value, color=variable), shape='+') +
#  stat_smooth(aes(stock, value, color=variable),
#    degree=0, se=FALSE, span=0.15) +
  ylab("Net Present Value")
````

### 2012-06-28 inst/examples/logistic_lognormal.Rmd
cleaner plots

ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value], color=variable), shape='+') +
	stat_smooth(aes(stock, stock-x_grid[value], color=variable), degree=1, se=FALSE) +
  ylab("escapement")

ggplot(policy) +
  geom_point(aes(stock, x_grid[value], color=variable), shape='+') +
	stat_smooth(aes(stock, x_grid[value], color=variable), degree=1, se=FALSE) +
  ylab("harvest")

@@

ggplot(value) + 
  geom_point(aes(stock, value, color=variable)) +
  stat_smooth(aes(stock, value, color=variable), degree=1, se=FALSE) +
  ylab("Net Present Value")
````

>>>>

ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value], color=variable), shape='+') +
	stat_smooth(aes(stock, stock-x_grid[value], color=variable), 
    degree=1, se=FALSE, span=0.3) +
  ylab("escapement")

ggplot(policy) +
  geom_point(aes(stock, x_grid[value], color=variable), shape='+') +
	stat_smooth(aes(stock, x_grid[value], color=variable),
    degree=1, se=FALSE, span=0.3) +
  ylab("harvest")

@@

ggplot(value) + 
  geom_point(aes(stock, value, color=variable), shape='+') +
#  stat_smooth(aes(stock, value, color=variable),
#    degree=0, se=FALSE, span=0.15) +
  ylab("Net Present Value")
````
